Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-10 manuscript/manuscript.tex
editing Ne section

which estimates the \vb{impact of selection} on allele frequency change between
the initial generation $0$ and some later generation $t$, which can be varied
to see how this quantity grows through time. \gc{When the covariances
  are positive this} measure can intuitively
  be understood as the relative fraction of allele frequency change normally
  thought of as ``drift" that is actually due to selection; the denominator of
  $G(t)$ is $\var(p_t - p_0)$, which under drift alone is proportional to
  $\nicefrac{1}{2 N_e}$. By measuring the contribution of temporal covariances
caused by selection, $G(t)$ looks at the fraction selection contributes to what
looks like a faster rate of drift, or lower $N_e$. Additionally, $G(t)$ can be
understood as a short-timescale estimate of the reduction in neutral diversity
due to linked selection (see Supplementary Materials Section
\ref{supp:reduction-approx}). Since \textcite{Barghi2019-qy} experiment is
sequenced every ten generations, in the numerator for the covariance we use the
allele frequency changes between adjacent timepoints, which are ten generations
apart; \vb{thus the strong covariances between adjacent generations are not
  observable and do not contribute to the numerator of $G(t)$}.
  \vb{Additionally, selection also inflates the variance in allele frequency
    change per generation; however, this effect cannot be easily distinguished
    from drift.} \vb{For both these reasons, our measure $G(t)$ is strongly
  conservative} (\vb{we demonstrate this through simulations in Supplementary
Material Section \ref{supp:tempblocks}}).  Still, we find a remarkably strong
signal. Greater than $20\%$ of total, genome-wide allele frequency change over
60 generations is the result of selection (Figure \ref{fig:figure-1} B).

>>>>

which estimates the \vb{impact of selection} on allele frequency change between
the initial generation $0$ and some later generation $t$, which can be varied
to see how this quantity grows through time. \gc{When the covariances
  are positive this} measure can intuitively
  be understood as the relative fraction of allele frequency change normally
  thought of as ``drift" that is actually due to selection.
  %SO much of this felt redundent  the denominator of
  %$G(t)$ is $\var(p_t - p_0)$, which under drift alone is proportional to
  %$\nicefrac{1}{2 N_e}$.
 %By measuring the contribution of temporal covariances
%caused by selection, $G(t)$ looks at the fraction selection contributes to what
%looks like a faster rate of drift, or lower $N_e$.
Additionally, $G(t)$ can be understood as a short-timescale estimate of the reduction in neutral diversity
due to linked selection (\gc{or equivalently the reduction in neutral effective
population size needed to account linked selection,} see Supplementary Materials Section
\ref{supp:reduction-approx}). Since \textcite{Barghi2019-qy} experiment is
sequenced every ten generations, in the numerator for the covariance we use the
allele frequency changes between adjacent timepoints, which are ten generations
apart; \vb{thus the strong covariances between adjacent generations are not
  observable and do not contribute to the numerator of $G(t)$}.
  \vb{Additionally, selection also inflates the variance in allele frequency
    change per generation; however, this effect cannot be easily distinguished
    from drift.} \vb{For both these reasons, our measure $G(t)$ is strongly
  conservative} (\vb{we demonstrate this through simulations in Supplementary
Material Section \ref{supp:tempblocks}}).  Still, we find a remarkably strong
signal. Greater than $20\%$ of total, genome-wide allele frequency change over
60 generations is the result of selection (Figure \ref{fig:figure-1} B).
